---
title: "HW 01 - Pet names"
author: "Julian Siegel"
date: "01/09/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

There are 52,519 pets in the data set.

### Exercise 2

There are 7 variables in the data set.

### Exercise 3

```{r common-names}
seattlepets %>%
  count(animal_name, sort = TRUE)
```
  
The three most common names are N/A, Lucy, and Charlie

### Exercise 4

```{r common-names-by-species}
seattlepets %>% 
  group_by(species) %>%
  count(animal_name, sort = TRUE)

seattlepets %>%
  count(species, sort = TRUE)

seattlepets %>% 
  group_by(species) %>%
  count(animal_name, sort = TRUE) %>% 
  slice_max(n, n = 5) %>% 
  arrange(species, n)
```

### Exercise 5

The names below the line are more common for cats than for dogs.

### Exercise 6

The relationship for the variables is positive because when a name is more common for a cat it will generally be more common for a dog or vice versa.